Hierarchical Dispatching and Overriding

### 2017-10-08 NewVersion/sections/Discussion.tex
S5 done.

Our formalization has already made abstract methods in a simple way. In other languages they may perform more complicated behaviours.
For instance, in Java 8 when putting two identical abstract methods together by multiple inheritance, there is no conflict error. We omit
that case for two reasons. First, our formalization just treats abstract methods as concrete methods with an empty body, and that simplifies
the rules and the proof a lot. Second, our design choice tends to give more sense on those interesting cases, just as we reject the diamond inheritance. The triangle inheritance should distinguish and treat differently on the two methods instead of fusing them, for they represent different operations, even if they are abstract.

@@

Fields as a particular non-orthogonal feature.

\subsection{More}

\paragraph{Diamond interface check, loosen the model}

\paragraph{Hierarchical Overriding Restriction, loosen the model.}
In \MIM{}, hierarchical overriding can only override an interface that defines the original method. But in reality, sometimes this condition is too restrict and can be relaxed to allowing overriding a super interface... And an override could be able to go over original methods. Pros \& cons.

\paragraph{Path Invocation}

\paragraph{(no example) Method Resolution Rules.}

\paragraph{(no example) better code reuse (more kinds of method invocation)}
Other resolution possibilities and comparison.

>>>>

Our formalization has already made abstract methods in a simple way. In other languages they may perform more complicated behaviours.
For instance, in Java 8 when putting two identical abstract methods together by multiple inheritance, there is no conflict error. We omit
that case for two reasons. First, our formalization just treats abstract methods as concrete methods with an empty body, and that simplifies
the rules and the proof a lot. Second, our design choice tends to give more sense on those interesting cases, just as we reject the simple case of diamond inheritance. The triangle inheritance should distinguish and treat differently on the two methods instead of fusing them, for they represent different operations, even if they are abstract.

@@

One typical non-orthogonal extension to our model could be to have fields. Having fields in OO multiple inheritance is a non-trivial issue. There has been a lot of work on it, such as C++ that uses virtual inheritance. The trait model simply disallows state to avoid that issue. In our language, however, we can perhaps borrow the idea of \textit{interface-based programming} [], which actually models state with abstract state operations. This can be realized by extending our current model with static methods and anonymous classes from Java. To directly support fields it requires more discussions and experiments, we leave them as our future work.

\subsection{Loosening the Model}

For the goal of simplifying the model and type soundness proof, we have added a few constraints in the minimal calculus. Our language simply rejects the diamond inheritance, see the example below:

\vspace{3pt}\begin{lstlisting}
interface A { void m() {...} }
interface B extends A { void m() {...} }
interface C extends A { void m() {...} }
interface D extends B, C {}
\end{lstlisting}\vspace{3pt}
In the example, both $B.m$ and $C.m$ override $A.m$, so we think they should represent the same operation. In that case, we believe that D inherits
both conflicting methods without an explicit override, and it is in fact an intention conflict. Our calculus rejects these intentional conflicts by rule \textsc{(T-Intf)}, where $D$ is considered to be ill-formed. Nonetheless, as a general-purpose language, C++ accepts the definition of $D$, but forbids a cast from $D$ to $A$ because of ambiguity. For the conciseness of the proof, our language is more conservative on interfaces.
But we could also loosen the model and perform ambiguity check on casts and other expressions.

Another case is about the restriction on hierarchical overrides. In our language model there are two types of methods (though they share the same syntax): original methods and hierarchical overrides. We require that a hierarchical override should only override an original method. Yet from the idea of encapsulation and modularity on programs, we could also allow an override to work on another override, which forms a series of overrides.

\haoyuan{more. 1) Path Invocation, more generalized diamond inheritance: not clear; other method resolution techniques: no example; better code reuse with other kinds of method invocation: no example. }
